acquisition of TEs

### 2021-02-26 Analyze_TEs_old.Rmd
Organized Simulations in order

@@

@@

```{r}
stacked <- keepers_ws_TE %>%
  select(baby_id, balance_vocab, word_vocab, number_of_te, Dom_unique_words, NonDom_unique_words) %>%
  arrange(desc(number_of_te)) %>%
  mutate(TE = number_of_te) %>%
  pivot_longer(-c(baby_id, balance_vocab, word_vocab, TE), 
               names_to = "Type", values_to = "NumberOfWords") %>%
  mutate(Type = factor(Type, levels=c("NonDom_unique_words", "Dom_unique_words", "number_of_te"))) %>%
  #Subset balance_vocab by 3 levels 
  mutate(BalSubset = cut(balance_vocab, breaks = 3, 
                         labels=c("HighBalance", "MidRangeBalance", "LeastBalance")))

LeastBal_plot <- stacked %>%
  filter(BalSubset == "LeastBalance") %>%
  ggplot(aes(x = reorder(baby_id, -NumberOfWords, sum), y = NumberOfWords)) +
  geom_col(aes(fill = Type)) +
  scale_fill_manual(values = c("#1f78b4", "#a6cee3", "#33a02c")) +
  scale_y_continuous(limits = c(0, 1050)) +
  labs(x = "Individual infant", 
       y = "Number of concepts produced",
       title = "Least balanced") + 
  theme(plot.title = element_text(hjust = 0.5))

MidRangeBal_plot <- stacked %>%
  filter(BalSubset == "MidRangeBalance") %>%
  ggplot(aes(x = reorder(baby_id, -NumberOfWords, sum), y = NumberOfWords)) +
  geom_col(aes(fill = Type)) +
  scale_fill_manual(values = c("#1f78b4", "#a6cee3", "#33a02c")) +
  scale_y_continuous(limits = c(0, 1050)) +
  labs(x = "Individual infant", 
       y = "Number of concepts produced",
       title = " ") + 
  theme(plot.title = element_text(hjust = 0.5))

HighBal_plot <- stacked %>%
  filter(BalSubset == "HighBalance") %>%
  ggplot(aes(x = reorder(baby_id, -NumberOfWords, sum), y = NumberOfWords)) +
  geom_col(aes(fill = Type)) +
  scale_fill_manual(values = c("#1f78b4", "#a6cee3", "#33a02c")) +
  scale_y_continuous(limits = c(0, 1050)) +
  labs(x = "Individual infant", 
       y = "Number of concepts produced",
       title = "High balance") + 
  theme(plot.title = element_text(hjust = 0.5))

Bal_StackedPlot <- ggarrange(LeastBal_plot, 
          MidRangeBal_plot + rremove("ylab"), 
          HighBal_plot + rremove("ylab"),
          ncol = 3, nrow = 1,
          common.legend = TRUE, legend="bottom")

>>>>

write.csv(keepers_ws_TE, "Data/keepers_ws_TE.csv", row.names = F)

@@

# Descriptives: Vocabulary measures
```{r}
## Mean word vocab size
keepers_ws_TE %>% 
  summarize(mean_W = mean(word_vocab, na.rm=T), 
            sd_W = sd(word_vocab, na.rm=T),
            min_W = min(word_vocab, na.rm=T),
            max_W = max(word_vocab, na.rm=T))

## Mean TE size
keepers_ws_TE %>% 
  summarize(mean_TE = mean(number_of_te, na.rm=T), 
            sd_TE = sd(number_of_te, na.rm=T),
            min_TE = min(number_of_te, na.rm=T),
            max_TE = max(number_of_te, na.rm=T))

## Mean unique word size
keepers_ws_TE %>% 
  summarize(mean_Du = mean(Dom_unique_words, na.rm=T), 
            sd_Du = sd(Dom_unique_words, na.rm=T),
            min_Du = min(Dom_unique_words, na.rm=T),
            max_Du = max(Dom_unique_words, na.rm=T))

keepers_ws_TE %>% 
  summarize(mean_Nu = mean(NonDom_unique_words, na.rm=T), 
            sd_Nu = sd(NonDom_unique_words, na.rm=T),
            min_Nu = min(NonDom_unique_words, na.rm=T),
            max_Nu = max(NonDom_unique_words, na.rm=T))

t.test(keepers_ws_TE$Dom_unique_words, keepers_ws_TE$NonDom_unique_words, 
       paired = TRUE) # paired-samples t-test to compare Du and Nu

## Stacked barchart to plot TE, Du, and Nu of individual infants (facet by balance)
stacked <- keepers_ws_TE %>%
  select(baby_id, balance_vocab, word_vocab, number_of_te, Dom_unique_words, NonDom_unique_words) %>%
  # Subset balance_vocab by 3 levels 
  mutate(BalSubset = cut(balance_vocab, breaks = 3, 
                         labels=c("MostBalanced", "MediumBalanced", "LeastBalanced"))) %>%
  arrange(desc(number_of_te)) %>%
  mutate(TE = number_of_te) %>%
  pivot_longer(-c(baby_id, balance_vocab, BalSubset, word_vocab, TE), 
               names_to = "Type", values_to = "NumberOfWords") %>%
  mutate(Type = factor(Type, levels=c("NonDom_unique_words", "Dom_unique_words", "number_of_te")))

LeastBal_plot <- stacked %>%.
  filter(BalSubset == "LeastBalanced") %>%
  ggplot(aes(x = reorder(baby_id, -NumberOfWords, sum), y = NumberOfWords)) +
  geom_col(aes(fill = Type)) +
  scale_fill_manual(values = c("#1f78b4", "#a6cee3", "#33a02c")) +
  scale_y_continuous(limits = c(0, 1050)) +
  labs(x = "Individual infant", 
       y = "Number of concepts produced",
       title = "Least balanced") + 
  theme(plot.title = element_text(hjust = 0.5))

MediumBal_plot <- stacked %>%
  filter(BalSubset == "MediumBalanced") %>%
  ggplot(aes(x = reorder(baby_id, -NumberOfWords, sum), y = NumberOfWords)) +
  geom_col(aes(fill = Type)) +
  scale_fill_manual(values = c("#1f78b4", "#a6cee3", "#33a02c")) +
  scale_y_continuous(limits = c(0, 1050)) +
  labs(x = "Individual infant", 
       y = "Number of concepts produced",
       title = "Medium balanced") + 
  theme(plot.title = element_text(hjust = 0.5))

MostBal_plot <- stacked %>%
  filter(BalSubset == "MostBalanced") %>%
  ggplot(aes(x = reorder(baby_id, -NumberOfWords, sum), y = NumberOfWords)) +
  geom_col(aes(fill = Type)) +
  scale_fill_manual(values = c("#1f78b4", "#a6cee3", "#33a02c")) +
  scale_y_continuous(limits = c(0, 1050)) +
  labs(x = "Individual infant", 
       y = "Number of concepts produced",
       title = "Most balanced") + 
  theme(plot.title = element_text(hjust = 0.5))

Bal_StackedPlot <- ggarrange(LeastBal_plot, 
          MediumBal_plot + rremove("ylab"), 
          MostBal_plot + rremove("ylab"),
          ncol = 3, nrow = 1,
          common.legend = TRUE, legend="bottom")

## Anova to compare the total vocab size among the 3 balance groups in the stacked barchart
stacked_wide <- keepers_ws_TE %>%
  select(baby_id, balance_vocab, word_vocab, concept_vocab, propTE, number_of_te, Dom_unique_words, NonDom_unique_words) %>%
  # Subset balance_vocab by 3 levels 
  mutate(BalSubset = cut(balance_vocab, breaks = 3, 
                         labels=c("MostBalanced", "MediumBalanced", "LeastBalanced")))

W_byB_anova <- aov(word_vocab ~ BalSubset, data = stacked_wide)
summary(W_byB_anova)

## Mean proportion of TE
stacked_wide %>% 
  filter(BalSubset == "LeastBalanced") %>%
  summarize(mean_propTE = mean(propTE, na.rm=T), 
            sd_propTE = sd(propTE, na.rm=T),
            min_propTE = min(propTE, na.rm=T),
            max_propTE = max(propTE, na.rm=T))

stacked_wide %>% 
  filter(BalSubset == "MediumBalanced") %>%
  summarize(mean_propTE = mean(propTE, na.rm=T), 
            sd_propTE = sd(propTE, na.rm=T),
            min_propTE = min(propTE, na.rm=T),
            max_propTE = max(propTE, na.rm=T))

stacked_wide %>% 
  filter(BalSubset == "MostBalanced") %>%
  summarize(mean_propTE = mean(propTE, na.rm=T), 
            sd_propTE = sd(propTE, na.rm=T),
            min_propTE = min(propTE, na.rm=T),
            max_propTE = max(propTE, na.rm=T))

## Correlation between concept vocab and TE across different balance group
stacked_wide_most <- stacked_wide %>%
  filter(BalSubset == "MostBalanced")

cor.test(stacked_wide_most$number_of_te, stacked_wide_most$concept_vocab, method = "pearson")

stacked_wide_med <- stacked_wide %>%
  filter(BalSubset == "MediumBalanced")

cor.test(stacked_wide_med$number_of_te, stacked_wide_med$concept_vocab, method = "pearson")

stacked_wide_least <- stacked_wide %>%
  filter(BalSubset == "LeastBalanced")

cor.test(stacked_wide_least$number_of_te, stacked_wide_least$concept_vocab, method = "pearson")

## Anova to compare the unique dom vocab size and unique non-dom vocab size among the 3 balance groups in the stacked barchart
stacked_wide %>% 
  group_by(BalSubset) %>%
  summarize(mean_Du = mean(Dom_unique_words, na.rm=T), 
            sd_Du = sd(Dom_unique_words, na.rm=T),
            min_Du = min(Dom_unique_words, na.rm=T),
            max_Du = max(Dom_unique_words, na.rm=T))

Du_byB_anova <- aov(Dom_unique_words ~ BalSubset, data = stacked_wide)
summary(Du_byB_anova)

pairwise.t.test(stacked_wide$Dom_unique_words, stacked_wide$BalSubset,
                 p.adjust.method = "BH")

stacked_wide %>% 
  group_by(BalSubset) %>%
  summarize(mean_Nu = mean(NonDom_unique_words, na.rm=T), 
            sd_Nu = sd(NonDom_unique_words, na.rm=T),
            min_Nu = min(NonDom_unique_words, na.rm=T),
            max_Nu = max(NonDom_unique_words, na.rm=T))

Nu_byB_anova <- aov(NonDom_unique_words ~ BalSubset, data = stacked_wide)
summary(Nu_byB_anova)

pairwise.t.test(stacked_wide$NonDom_unique_words, stacked_wide$BalSubset,
                 p.adjust.method = "BH")
```

@@
